The Impact of Education <br>

### 2014-12-04 Presentation/EdEntrePres.Rmd
Updated slides

*Text from Thierry*

@@

@@

- Data availability prevented us from using PISA data for this project

@@

- GEM: Global Entrepreneurship Monitor project is an annual assessment of the entrepreneurial activity, aspirations, and attitudes of individuals across a wide range of countries.

-

@@

*How is it measured*

>>>>

What determines entrepreneurship?  
Economic and structural factors - Already searched
Educational and cultural factors - Hardly searched

Even when focused on attitudes / Entrepreneurship,  
Studies look more at what attitudes are favourable  
Almost none searched what determines these attitudes.

@@

Education System that reinforces Self-confidence

Higher degree of individual self-esteem

Higher probability an individual becomes an entrepreneur

Higher rate of entrepreneurship at a country-level

@@

- Data availability prevented us from using PISA data for this project. For instance, for 2015 PISA will be looking at science education.

@@

- The Global Entrepreneurship Monitor project is an annual assessment of the entrepreneurial activity, aspirations, and attitudes of individuals across a wide range of countries.

- Only 10 countries at first, now covering 75% of world population and 89% of world GDP

- GEM is being used is regularly refered to in research, including in OECD reports.

- GEM uses primary data collection which results in massive comprehensive datasets. That is the 2001-2010 multi-year APS Database covers over 1.3 million observations over 85 countries.

- APS or Adult Population Survey (at least 2000 sample size) looks at activity, attitudes and aspirations.

- NES or National Expert Survey looks at 9 entrepreneurial framework conditions (4 national experts for each)

@@

In the absence of indicator directly aligned with our research design, we turned to an item of the NES survey as a proxy, D01:

"In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative"

But there is a clear lack of consistency in the data.

Many flaws : scale, methodology for collection (poor time management, personal connections)
